In the previous section we described several methods for GP regression and
classification. All these methods have different limitations. Standard methods
can not be applied for big datasets, KISS-GP requires small dimensionality of
the feature space and other methods based on inducing points are limited to use
a small number $m$ of these points. In this section we propose the TT-GP method
that can be used with big datasets and can incorporate billions of inducing
inputs. TT-GP can naturally be used for training expressive deep kernels to work
with structured data (e.g. images).

\subsection{Variational Parameters Approximation}
  In section \ref{inducing_inputs} we derived the variational lower bound of
  \citet{hensman2013}. We will place the inducing inputs $Z$ on a
  multidimensional grid in the feature space and we will assume the
  covariance function satisfies (\ref{prod_kernel}). Let the number
  of inducing points in each dimension be $m_0$. Then
  \[
    m = m_0^D.
  \]
  As shown in section \ref{kiss_gp},
  in this case $\Kmm$ matrix can be rewritten as a Kronecker product over
  dimensions. Substituting the approximation (\ref{kernel_interpolation}) into
  the lower bound (\ref{elbo_reg}), we obtain
  \begin{equation}
  \label{kissgp_elbo}
    \begin{split}
      \log p(y) \ge
      \sum_{i=1}^n \left ( \log \N (y_i | w_i^T \mu, \nu^2) -
        \frac 1 {2\nu^2} \tilde K_{ii} -
        \frac 1 {2\nu^2} \tr (w_i^T \Sigma w_i)
      \right )-
      \\
      - \frac 1 2 \left(
        \log \frac {|\Kmm|} {|\Sigma|} - m + \tr(\Kmm^{-1} \Sigma) +
        \mu^T \Kmm^{-1} \mu
      \right),
    \end{split}
  \end{equation}
  where $\tilde K_{ii} = k(x_i, x_i) - w_i^T \Kmm w_i$.

  Note that $\Kmm^{-1}$ and $|\Kmm|$ can be computed with
  $\bigO(D m_0^3) = \bigO(D m^{3/D})$ operations due to the
  Kronecker product structure. Now the most computationally demanding terms
  are those containing variational parameters $\mu$ and $\Sigma$.

  Let us restrict the family of variational distributions (\ref{var_family}). Let $\Sigma$ be
  a Kronecker product over dimensions, and $\mu$ be in TT-format with TT-ranks
  not greater than $r$. Then, according to section \ref{tensor_train}, we can
  compute the lower bound~\eqref{kissgp_elbo} with
  $\bigO(nDm_0 r^2 + D m_0 r^3 + Dm_0^3) =
  \bigO(nD m^{1/D} r^2 + D m^{1/D} r^3 + D m^{3/D}).$

  Thus, the proposed TT-GP method has linear complexity with respect to dimensionality
  $D$ of the feature space, despite the exponential growth of the number of
  inducing inputs. Lower bound  (\ref{kissgp_elbo})
  can be maximized with respect to kernel hyper-parameters $\theta$, TT-cores
  of $\mu$ and Kronecker multipliers of $\Sigma$. Note that stochastic optimization
  can be applied, as the bound (\ref{kissgp_elbo}) factorizes over data points.

\subsection{Classification}

  In this section we describe a generalization of the proposed method for
  multiclass classification. In this case the dataset consists of features
  $X = (x_1, x_2, \ldots, x_n)^T \in \R^{n \times D}$ and target values
  $y = (y_1, y_2, \ldots, y_n)^T \in \{1, 2, \ldots, C\}^n$, where $C$ is the
  number of classes.

  Consider $C$ Gaussian processes taking place in $\R^D$. Each process
  corresponds to it's own class. We will place $m = m_0^D$ inducing points $Z$ on a grid
  in the feature space, and they will be shared between all processes. Each
  process has it's own set of latent variables representing the values of
  the process at data points $f^c \in \R^n$, and inducing inputs $u^c \in \R^m$.
  We will use the following model
  \[
    p(y, f, u) = \prod_{i=1}^n p(y_i | f_i^{1, 2, \ldots, C})
      \prod_{c=1}^C p(f^c | u^c) p(u^c),
  \]
  where $p(f^c | u^c)$ and $p(u^c)$ are defined as in (\ref{priors}) and $p(y_i | f_i^{1,2, \ldots, C}) = \exp(f_i^{y_i}) / (\sum_{j=1}^C\exp(f_i^j))$.
  
  We will use variational distributions of form
  \[
    q(f^1, f^2, \ldots, f^C, u^1, u^2, \ldots, u^C) =
    q(f^1, u^1) \cdot q(f^2, u^2) \cdot \ldots \cdot q(f^C, u^C),
  \]
  where $q(f^c, u^c) = p(f^c | u^c) \N(u^c | \mu^c, \Sigma^c)\ c=1, 2, \ldots, C$ and all $\mu^c$ are represented in TT-format with TT-ranks not greater than $r$,
  $\Sigma^c$ are represented as Kronecker products over dimensions. Similarly to (\ref{main_elbo}), we obtain
  \begin{equation}
  \label{elbo_multiclass}
    \log p(y) \ge \sum_{i = 1}^n \E_{q(f_i^{1, 2, \ldots, C})} \log p(y_i | f_i^{1, 2, \ldots, C})
      - \sum_{c = 1}^{C} \KL(q(u_c) || p(u_c))
  \end{equation}
  The second term in (\ref{elbo_multiclass}) can be computed analytically as
  a sum of KL-divergences between normal distributions. The first term is
  intractable. In order to approximate the first term we will use a lower bound.
  Let $y_i$ belong to class $c$. Then, we can rewrite
  \begin{equation}
  \label{expectation_term}
    \E_{q(f_i^{1, 2, \ldots, C})} \log p(y_i | f_i^{1, 2, \ldots, C}) =
    \E_{q(f_i^c)} f_i^c - \E_{q(f_i^{1, 2, \ldots, C})}
    \log \biggl(\sum_{j=1}^C \exp (f_i^j) \biggr),
  \end{equation}
  where $q(f_i^{1, 2\ldots, C}) = \N(f^1 | m_i^1, s_i^1)\cdot \N(f^2| m_2, s_i^2) \cdot \ldots \cdot \N(f^C | m_i^C, s_i^C)$.

  The first term in (\ref{expectation_term}) is obviously tractable, while the
  second term has to be approximated. \citet{bouchard2007} discusses several
  lower bounds for expectations of this type. Below we derive one of these bounds,
  which we use in TT-GP.

  Concavity of logarithm implies $\log(\sum_{j=1}^{C} \exp(f_i^j)) \le \varphi \sum_{j=1}^C \exp(f_i^j) - \log \varphi - 1,\ \forall\varphi > 0$. Taking expectation of both sides of the inequality and minimizing with respect
  to $\varphi$, we obtain
  \begin{equation}
  \label{bouchard_bound}
    \E_{q(f_i^{1, 2, \ldots, C})} \log\biggl(\sum_{j=1}^C \exp(f_i^j)\biggr) \le
    \log \biggl(\sum_{j=1}^C \exp\bigl(m_i^j + \frac 1 2 s_i^j\bigr) \biggr).
  \end{equation}
  Substituting (\ref{bouchard_bound}) back into (\ref{elbo_multiclass}) we obtain
  a tractable lower bound for multiclass classification task, that can be
  maximized with respect to kernel hyper-parameters $\theta^c$, TT-cores of
  $\mu^c$ and Kronecker factors of $\Sigma^c$. The complexity of the method
  is $C$ times higher, than in regression case.

\subsection{Deep kernels}

  \citet{wilson2016stochastic} and \citet{wilson2016deep} showed the efficiency
  of using expressive kernel functions based on deep neural networks with
  Gaussian processes on a variety of tasks. The proposed TT-GP method is
  naturally compatible with this idea.

  Consider a covariance function $k$ (satisfying (\ref{prod_kernel})) and
  a neural network (or in fact any parametric transform) $net$. We can define a
  new kernel as follows
  \[
    k_{net}(x, x') = k(net(x), net(x')).
  \]
  We can train the neural network weights through maximization of GP marginal
  likelihood, the same way, as we normally train kernel hyper-parameters $\theta$.
  This way, the network learns a multidimensional embedding for the data, and
  the GP is making the prediction working with this embedding.
  \citet{wilson2016stochastic} trained one-dimensional GPs on different outputs
  of the network. TT-GP allows us to train Gaussian processes on all network
  outputs, and train the whole model end-to-end without pretraining.
